API design for machine learning software: experiences from the scikit-learn project

### 2013-06-24 paper.tex
rename sections; make forward referencing correct

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead focus on an
in-depth discussion and analysis of the design choices made when building the
library. We first present in section \ref{sec:core-api} the central application
programming interface (API) and then describe, in section \ref{sec:advanced-api},
advanced API mechanisms built from the core interface. Section
\ref{sec:implementation} briefly describes the implementation.
Section \ref{sec:comparison} then
compares \emph{scikit-learn} to other major projects in terms of API. Finally,
conclusions and directions of future works are included in section
\ref{sec:conclusions}.

@@

\section{Future Work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Topics like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

@@

\section{Conclusions and future work}
\label{sec:conclusions}

>>>>

In a previous paper \citep{pedregosa2011}, \sklearn was briefly presented and
benchmarked against several competitors. In this paper, we instead focus on an
in-depth discussion and analysis of the design choices made when building the
library. We first present in section \ref{sec:core-api} the central application
programming interface (API) and then describe, in section \ref{sec:advanced-api},
advanced API mechanisms built from the core interface. Section
\ref{sec:implementation} briefly describes the implementation.
Section \ref{sec:comparison} then
compares \emph{scikit-learn} to other major projects in terms of API.
Section \ref{sec:future_work} outlines some of the work to be done before
the scikit-learn 1.0 release.  Finally, we summarize and conclude in
section \ref{sec:conclusions}.

@@

\section{Future Work}
\label{sec:future_work}
There are several problems with the current scikit-learn interface which
will be resolved in the future.
At present, the library does not support some classical machine learning tasks,
including neural networks, ensemble meta-estimators for
bagging or subsampling strategies and missing value completion algorithms.
Topics like structured prediction or reinforcement learning are
considered off-topic for the project, since they would require quite different
data representations and APIs.

@@

\section{Conclusion}
\label{sec:conclusions}
